Investigation on GIT

### 2010-04-25 paper.tex
cambie unos detalles de lo que subio bruno pa que compile

When we want to share our work with the rest of the team we have two basic concepts, Push & Pull
Push refers to taking all my changes and add them to the repository of another co-worker. But in practice we don't do this becouse we shouldn't make a push on a co-worker working copy, instead it, we make Push in a "central repository" where all team make their Pushes too, this logic is similar to traditional VCS, but we need to keep in mind that we could have a lot of "central repositorys" for different parts of our project.
Pull is a compose action of fetch + merge, where fetch takes the changes from selected repository of a co-worker and copy them to my local repository, merge obiously merges those changes with the sourcecode of my local repository
At the same way, another co-worker can do Pull over my working copy and get my new code & changes without any problem.

>>>>

When we want to share our work with the rest of the team we have two basic concepts, Push and Pull
Push refers to taking all my changes and add them to the repository of another co-worker. 
But in practice we don't do this becouse we shouldn't make a push on a co-worker working copy, 
instead it, we make Push in a "central repository" where all team make their Pushes too, 
this logic is similar to traditional VCS, but we need to keep in mind that we could have a 
lot of "central repositorys" for different parts of our project.
Pull is a compose action of fetch + merge, where fetch takes the changes from selected 
repository of a co-worker and copy them to my local repository, merge obiously merges those 
changes with the sourcecode of my local repository
At the same way, another co-worker can do Pull over my working copy and get my new code and 
changes without any problem.
